---
title: "Introduction to dplyr"
author: "zero"
date: "6/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(gapminder)
library(tidyverse)

```

## Use filter() to subset data row-wise
```{r}
sub_gapmind <- gapminder %>% 
  filter(., country == "Rwanda", year > 1979) 
  
filter(gapminder, country %in% c("Rwanda","Afghanistan"))

```


## Use select() to subset the data on variables or columns
```{r}
sub_gapmind_01 <- gapminder %>% 
  select(., year, lifeExp) %>% 
  head(6)

```
## Use mutate() to add new variables
```{r}
(my_gapminder <- gapminder)
my_gapminder %>% 
  mutate(.,gdp = pop * gdpPercap)
```

## Use arrange() to row-order data in a principled way
```{r}
my_gapminder %>% 
  arrange(.,year,country)
my_gapminder %>% 
  filter(.,year == 2007) %>% 
  arrange(.,desc(lifeExp))
```

## Use rename() to rename variables
```{r}
my_gapminder %>% 
  rename(.,
         life_exp = lifeExp,
         gdp_percap = gdpPercap)
```

## select() can rename and reposition variables
```{r}
my_gapminder %>% 
  filter(country == "Burundi", year > 1996) %>% 
  select(yr = year, lifeExp, gdpPercap) %>% 
  select(gdpPercap, everything())

```

## group_by() is a mighty weapon
```{r}
my_gapminder %>% 
  group_by(continent) %>% 
  #summarise(num = n())
  tally()
my_gapminder %>% 
  #group_by(continent) %>% 
  count(continent)
```

### general summarization
```{r}
my_gapminder %>% 
  group_by(continent) %>% 
  summarise_each(n = n(),
            avg = mean(lifeExp))
library(stringr)

my_gapminder %>%
  filter(continent %in% c("Africa","Asia"),year %in% c(1952, 2007)) %>%
  group_by(continent) %>%
  summarise_each(funs(mean,sd), lifeExp) %>% # 函数的参数怎么设置呢？
  mutate(tongji = str_c(mean, "±", sd)) %>% 
  select(continent,tongji) 

```

## Grouped mutate
### Computing with group-wise summaries
### Window functions
















